---
title: "Penguins ANOVA"
author: "Lydia Bleifuss"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data 

```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our Question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie) 

2. Do some exploirng

New Functions: with + table for easy counting over multiple factors

Update species name use ing case_when

```{r}
counts <- with(penguins, table(species,sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie")
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

```

- Exploratory graphs
- Summary Statistics
- Levene's tests for equal variances
- one-way ANOVA
- post-hoc testing 

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) +
  facet_wrap(~ common_name)

hists

qqs <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq()+
  facet_wrap(~common_name)

qqs

#f-test

#We'll use the function leveneTest from the 'car' package 

#H0: Variances are equal
#HA: Variances are not equal 

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

#We retain the null hypothesis of equal variances (p = 0.06)

variances <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )

variances

```

#3. One-way ANOVA

Single factor: common_name (species)
Number of levels in the factor: 3 (Chinstrap, Gentoo, Adelie)
Random varialbe: flipper_length (mm)

Is there a significant difference in mean flipper length (mm) for femal Chinstrap, Gentoo and Adelie penguins? 

```{r}
#H0: Mean flipper lengths across all species are equal
#HA: At LEAST two means differ significantly

penguin_aov <- aov(flipper_length ~ common_name, data = penguins2)
summary(penguin_aov)

#At least two samples were taken from populations with different means.Which ones are different? All three are different from each other? Or something else? 

# Post_hoc testing using Tukey's HSD

penguin_ph <- TukeyHSD(penguin_aov)
penguin_ph


```
Mean flipper lengths for Adelie, Gentoo, and Chinstrap penguins are all significantly different (F(df) = statistic, p < 0.001, $\alpha$ = 0.05 with post-hoc Tukey's HSD, $\alpha = 0.05$.
