---
title: "Penguins ANOVA"
author: "Lydia Bleifuss"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read-in penguins.csv data 

```{r, include = FALSE}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")
```

Our Question:

Is there a significant difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie) 

2. Do some exploirng

New Functions: with + table for easy counting over multiple factors

Update species name use ing case_when

```{r}
counts <- with(penguins, table(species,sex))

penguins2 <- penguins %>% 
  mutate(common_name = 
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie")
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

```

- Exploratory graphs
- Summary Statistics
- Levene's tests for equal variances
- one-way ANOVA
- post-hoc testing 

